---
title: "thesis"
author: "Yuanzhao Wang"
date: "2/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
options(java.parameters = "-Xmx4G")
```

## Load libraries

```{r setup, message=FALSE}
library(r5r)
library(tidyverse)
library(sf)
library(irr)
library(ggthemes)
library(jtools)
library(gridExtra)
library(units)
library(ggspatial)
library(tibble)
library(modelr)
```



## Inter-rater reliability
```{r read csv, message=FALSE, warning=FALSE, results='hide'}
reliability <- read_csv("reliability_test.csv")
```

## IPercentage agreement
```{r, message=FALSE, warning=FALSE, results='hide'}
ratings <- reliability %>% select(lei, YZ, TW)
agree(ratings)
```

```{r, message=FALSE, warning=FALSE, results='hide'}
ratings_ai <- reliability %>% select(AI, lei)
kappa2(ratings_ai)
```

## Load spatial datasets and add ID columns

```{r dataset, message=FALSE, warning=FALSE, results='hide'}
boundary <- st_read("Largefiles/ad_boundary/boundary.shp")
centralarea <- st_read("Largefiles/centralarea/centralarea.shp")

school <- st_read("Largefiles/school/school.shp") %>% 
  st_transform("WGS84") 

hospital <- st_read("Largefiles/hospitals/Jiaxing_hos.shp") %>% 
  st_transform("WGS84")

busstop <- st_read("Largefiles/busstop/Jiaxing_busstop.shp") %>% 
  st_transform("WGS84")

restaurant <- st_read("Largefiles/restaurants/Jiaxing_res.shp") %>% 
  st_transform("WGS84")
  
greenspace <- st_read("Largefiles/greenspace/greenspace.shp") %>% 
  st_transform("WGS84")

leis <- st_read("Largefiles/leisure/yule.shp") %>% 
  st_transform("WGS84")

public <- st_read("Largefiles/public_service/shenghuo.shp") %>% 
  st_transform("WGS84")
  
shopping <- st_read("Largefiles/shopping/shopping.shp")
  
weibo <- st_read("Largefiles/weibo_wea/added_weibo.shp")

pl_restaurant <- st_read("planned/sample_pl_res.shp") %>% 
  st_transform("WGS84")

# existing zoning and planned zoning (bueiness, educational, greenspace, medical and residential)

ex_business <- st_read("Largefiles/existingplanning/ex_business.shp") %>% 
  st_transform("WGS84")

ex_educational <- st_read("Largefiles/existingplanning/ex_educational.shp") %>% 
  st_transform("WGS84")

ex_greenspace <- st_read("Largefiles/existingplanning/ex_greenspace.shp") %>% 
  st_transform("WGS84")

ex_medical <- st_read("Largefiles/existingplanning/ex_medical.shp") %>% 
  st_transform("WGS84")

ex_residential <- st_read("Largefiles/existingplanning/ex_residential.shp") %>% 
  st_transform("WGS84")

pl_business <- st_read("Largefiles/futureplanning/pl_business.shp") %>% 
  st_transform("WGS84")

pl_educational <- st_read("Largefiles/futureplanning/pl_educational.shp") %>% 
  st_transform("WGS84")

pl_greenspace <- st_read("Largefiles/futureplanning/pl_greenspace.shp") %>% 
  st_transform("WGS84")

pl_medical <- st_read("Largefiles/futureplanning/pl_medical.shp") %>% 
  st_transform("WGS84")

pl_residential <- st_read("Largefiles/futureplanning/pl_residential.shp") %>% 
  st_transform("WGS84")

hospital$Id <- NULL
restaurant$Id <- NULL
  
school <- school %>%
    mutate(id = seq(1, length(school$Name)))
restaurant <- restaurant %>%
    mutate(id = seq(1, length(restaurant$geometry)))
greenspace <- greenspace %>%
    mutate(id = seq(1, length(greenspace$Name)))
hospital <- hospital %>%
    mutate(id = seq(1, length(hospital$geometry)))
weibo <- weibo %>%
    mutate(id = seq(1, length(weibo$geometry)))
shopping <- shopping %>%
    mutate(id = seq(1, length(shopping$geometry)))
public <- public %>%
    mutate(id = seq(1, length(public$geometry)))
leis <- leis %>%
    mutate(id = seq(1, length(leis$geometry)))
pl_restaurant <- pl_restaurant %>%
    mutate(id = seq(1, length(pl_restaurant$geometry)))
ex_business <- ex_business %>%
    mutate(id = seq(1, length(ex_business$geometry)))
ex_educational <- ex_educational %>%
    mutate(id = seq(1, length(ex_educational$geometry)))
ex_greenspace <- ex_greenspace %>%
    mutate(id = seq(1, length(ex_greenspace$geometry)))
ex_medical <- ex_medical %>%
    mutate(id = seq(1, length(ex_medical$geometry)))
ex_residential <- ex_residential %>%
    mutate(id = seq(1, length(ex_residential$geometry)))
pl_business <- pl_business %>%
    mutate(id = seq(1, length(pl_business$geometry)))
pl_educational <- pl_educational %>%
    mutate(id = seq(1, length(pl_educational$geometry)))
pl_greenspace <- pl_greenspace %>%
    mutate(id = seq(1, length(pl_greenspace$geometry)))
pl_medical <- pl_medical %>%
    mutate(id = seq(1, length(pl_medical$geometry)))
pl_residential <- pl_residential %>%
    mutate(id = seq(1, length(pl_residential$geometry)))
```

## Plot street network with hospital locations 

```{r, message=FALSE, warning=FALSE, results='hide'}
jiaxing_streets <- st_read("jiaxing/osmdata_network_01.pbf", layer = "lines", quiet=TRUE)
greenspace_points <- st_centroid(greenspace)

ggplot(jiaxing_streets) +
  geom_sf() +
  geom_sf(data = hospital, color = "red") +
  theme_void()
```

## Clip street network and layer of Weibo posts to city boundary

```{r CLIP, echo=FALSE}
jiaxing_streets <- jiaxing_streets[boundary,]
weibo_clip <- weibo[boundary,]
```

## Create grid

```{r build grid, echo=FALSE}
grid <- st_sf(st_make_grid(boundary, square = FALSE,
                           n = c(100, 100),
                           what = "polygons")) %>% 
  st_filter(boundary)

colnames(grid) <- "geometry"
st_geometry(grid) <- "geometry"

grid <- grid %>% 
  mutate(id = seq(1, length(grid$geometry), by = 1))


ggplot() +
  geom_sf(data = grid)+
  theme_map()

grid_points <- st_centroid(grid)
ggplot() +
  geom_sf(data = grid_points, size = 0.75) +
  geom_sf(data = weibo_clip, color = "red") +
  theme_map()
```

## get number of each type of destination in each grid cell

```{r}
grid <- grid %>%
  mutate(num_restaurant = lengths(st_covers(grid, restaurant))) %>%
  mutate(num_school = lengths(st_covers(grid, school)))%>%
  mutate(num_hospital = lengths(st_covers(grid, hospital)))%>%
  mutate(num_busstop = lengths(st_covers(grid, busstop)))%>%
  mutate(num_greenspace = lengths(st_covers(grid, greenspace_points)))%>%
  mutate(num_leis = lengths(st_covers(grid, leis)))%>%
  mutate(num_public = lengths(st_covers(grid, public)))%>%
  mutate(num_shopping = lengths(st_covers(grid, shopping)))%>%
  mutate(num_pl_restaurant = lengths(st_covers(grid,pl_restaurant)))

grid_points <- st_centroid(grid)

```


## run r5r

```{r, message=FALSE}
r5r_core <- setup_r5("jiaxing", verbose = FALSE)

```
## Run accessibility for each amenities, then use the Loop model for each of the threshold values and see which threshold gives the best model fit.

## Run this individually for each of the amenities, and then use the variable that gives the best fit for each to combine into a refined regression model.


This will add five columns to weibo_clip:

restaurant_access_5: The number of restaurants within a 5-minute walk.
restaurant_access_10: The number of restaurants within a 10-minute walk.
restaurant_access_15: The number of restaurants within a 15-minute walk.
restaurant_access_20: The number of restaurants within a 15-minute walk.
restaurant_access_25: The number of restaurants within a 15-minute walk.

`for (i in seq(5, 25, by = 5))` means you want to generate values for cutoffs that range from 5 to 25 minutes, increasing in increments of 5 minutes. You can get more columns by editing that line to get a wider range and/or increase by smaller increments.


# Accessibility from weibo posted to nearest restaurant

```{r, message=FALSE, results='hide'}
for (i in seq(5, 25, by=5)) {
  restaurant_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_restaurant",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(restaurant_access) <- c("id",
                                   paste("restaurant_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(restaurant_access)
}
  
```
# the Loop model
```{r}
formula <- as.formula(paste("positive_p ~ restaurant_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 25, by=5)) {
  formula <- as.formula(paste("positive_p ~ restaurant_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()
```

# ```{r}
# myplot <- ggplot(weibo_clip) +
#   geom_sf(data = jiaxing_streets, alpha = 0.2) +
#   geom_sf(aes(color = restaurant_access_15), size = 0.1) +
#   scale_color_viridis_c() +
#   theme_map()
# 
# pdf("ggplot.pdf")
# print(myplot)
# dev.off() 
# ```

# ```{r}
# ggplot(weibo_clip) +
#   geom_sf(aes(color = positive_p), size = 0.1) +
#   scale_color_viridis_c() +
#   theme_map()
# ```

# accessibility from weibo posted to greenspace

```{r, message=FALSE, results='hide'}
for (i in seq(5, 60, by=5)) {
  greenspace_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_greenspace",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(greenspace_access) <- c("id",
                                   paste("greenspace_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(greenspace_access)
}

```

```{r}
formula <- as.formula(paste("positive_p ~ greenspace_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 60, by=5)) {
  formula <- as.formula(paste("positive_p ~ greenspace_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()
```
# accessibility from weibo posted to school

```{r, message=FALSE, results='hide'}
for (i in seq(5, 30, by=5)) {
  school_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_school",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(school_access) <- c("id",
                                   paste("school_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(school_access)
}

  
formula <- as.formula(paste("positive_p ~ school_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 30, by=5)) {
  formula <- as.formula(paste("positive_p ~ school_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()

```

# accessibility from weibo posted to hospital

```{r, message=FALSE, results='hide'}
for (i in seq(5, 30, by=5)) {
  hospital_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_hospital",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(hospital_access) <- c("id",
                                   paste("hospital_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(hospital_access)
}
  
formula <- as.formula(paste("positive_p ~ hospital_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 30, by=5)) {
  formula <- as.formula(paste("positive_p ~ hospital_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()

```
# accessibility from weibo posted to busstop

```{r, message=FALSE, results='hide'}
for (i in seq(5, 90, by=5)) {
  busstop_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_busstop",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(busstop_access) <- c("id",
                                   paste("busstop_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(busstop_access)
}
  
formula <- as.formula(paste("positive_p ~ busstop_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 90, by=5)) {
  formula <- as.formula(paste("positive_p ~ busstop_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()

```
# accessibility from weibo posted to leis

```{r, message=FALSE, results='hide'}
for (i in seq(5, 30, by=5)) {
  leis_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_leis",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(leis_access) <- c("id",
                                   paste("leis_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(leis_access)
}
  
formula <- as.formula(paste("positive_p ~ leis_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 30, by=5)) {
  formula <- as.formula(paste("positive_p ~ leis_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()

```
# accessibility from weibo posted to public

```{r, message=FALSE, results='hide'}
for (i in seq(5, 30, by=5)) {
  public_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_public",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(public_access) <- c("id",
                                   paste("public_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(public_access)
}
  
formula <- as.formula(paste("positive_p ~ public_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 30, by=5)) {
  formula <- as.formula(paste("positive_p ~ public_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()

```
# accessibility from weibo posted to shopping

```{r, message=FALSE, results='hide'}
for (i in seq(5, 30, by=5)) {
  shopping_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_shopping",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(shopping_access) <- c("id",
                                   paste("shopping_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(shopping_access)
}
  
formula <- as.formula(paste("positive_p ~ shopping_access_", 5, sep=""))
model <- lm(formula, data = weibo_clip)

fit <- tibble(threshold = 5,
              fit = summary(model)$r.squared)

for (i in seq(10, 30, by=5)) {
  formula <- as.formula(paste("positive_p ~ shopping_access_", i, sep=""))
  model <- lm(formula, data = weibo_clip)

fit <- rbind(fit, c(i, summary(model)$r.squared))

  
}
fit

ggplot(fit, aes(x = threshold, y = fit)) +
  geom_point() +
  theme_bw()

```

```{r}
write_csv(weibo_clip, file = "weibo_clip.csv")
```


# Start here!



```{r}
weibo_clip <- read_csv("weibo_clip.csv")
```


## Comparison between the 15-min accessibility regression model and refined regression model with best threshold
```{r}

full1_model <- lm(positive_p ~ restaurant_access_15 + school_access_15 + hospital_access_15 + busstop_access_15 + greenspace_access_15 + leis_access_15 + public_access_15 + shopping_access_15, data = weibo_clip)

summary(full1_model)


full2_model <- lm(positive_p ~ restaurant_access_15 + school_access_25 + hospital_access_25 + busstop_access_70 + greenspace_access_25 + leis_access_20 + public_access_15 + shopping_access_25, data = weibo_clip)

summary(full2_model)

coeff_names <- c("Costant" = "(Intercept)")

export_summs(full1_model, full2_model,
             error_format = "(p = {p.value})",
             error_pos = "same",
             model.name = c ("Initial",
                             "Refined"),
             coef=coeff_names)
```
# ```{r}
# weibo_clip <- weibo_clip %>%
#  mutate(log_greenspace = log(greenspace_access), base = 2)
# 
# full_model2 <- lm(positive_p ~ restaurant_access + school_access + hospital_access + busstop_access + log_greenspace + leis_access + public_access + shopping_access, data = weibo_clip)
# 
# summary(full_model2)
# ```

## Regression models adding Types of day(Weekday, Weekend and holiday), 
## weather (Rainy, Cloudy, snow, smog and sunny), 
## and timeslots (early morning, morning, afternoon, sunset, everning and midnight)

```{r Regression analysis}

weibo_clip <- weibo_clip %>%
  filter(Timeslot != "?") %>%
  mutate(Timeslot = as.factor(Timeslot)) %>%
  mutate(Timeslot = relevel(Timeslot, ref = "Evening" ))%>%
  mutate(Type = as.factor(Type)) %>%
  mutate(Type = relevel(Type, ref = "Weekday" ))


full1_model <- lm(positive_p ~ restaurant_access_15 +
                    school_access_15 + hospital_access_15 +
                    busstop_access_15 + greenspace_access_15 +
                    leis_access_15 +
                    public_access_15 +
                    shopping_access_15,
                    data = weibo_clip)

summary(full1_model)


full2_model <- lm(positive_p ~ restaurant_access_15 +
                    school_access_25 +
                    hospital_access_25 +
                    busstop_access_70 +
                    greenspace_access_25 +
                    leis_access_20 +
                    public_access_15 +
                    shopping_access_25,
                    data = weibo_clip)

full3_model <- lm(positive_p ~ restaurant_access_15 +
                    school_access_25 +
                    hospital_access_25 +
                    busstop_access_70 +
                    greenspace_access_25 +
                    leis_access_20 +
                    public_access_15 +
                    shopping_access_25 +
                    Type +
                    Timeslot +
                    Weather,
                    data = weibo_clip)
coeff_names <- c("Costant" = "(Intercept)")

export_summs(full1_model, full2_model, full3_model,
             error_format = "(p = {p.value})",
             error_pos = "same",
             model.name = c ("Initial",
                             "Refined2",
                             "Refined3"),
             coef=coeff_names)
```
## Interaction analysis with specific Types, Timeslots and Weather
#Find out Types and Weather did not affect the results, but Timeslots mattered.

```{r Interaction analysis}

# Type1_model <- lm(positive_p ~ restaurant_access_15 +
#                     school_access_25 +
#                     hospital_access_25 +
#                     busstop_access_70 +
#                     greenspace_access_25 +
#                     leis_access_20 +
#                     public_access_15 +
#                     shopping_access_25 +
#                     Type +
#                     Timeslot +
#                     Weather +
#                     Type:restaurant_access_15,
#                     data = weibo_clip)
#                   
# summary(Type1_model)

Timeslot1_model <- lm(positive_p ~ restaurant_access_15 +
                    school_access_25 +
                    hospital_access_25 +
                    busstop_access_70 +
                    greenspace_access_25 +
                    leis_access_20 +
                    public_access_15 +
                    shopping_access_25 +
                    Type +
                    Timeslot +
                    Weather +
                    Timeslot:restaurant_access_15,
                    data = weibo_clip)
                  
summary(Timeslot1_model)

Timeslot2_model <- lm(positive_p ~ restaurant_access_15 +
                    school_access_25 +
                    hospital_access_25 +
                    busstop_access_70 +
                    greenspace_access_25 +
                    leis_access_20 +
                    public_access_15 +
                    shopping_access_25 +
                    Type +
                    Timeslot +
                    Weather +
                    Timeslot:school_access_25,
                    data = weibo_clip)
                  
summary(Timeslot2_model)

Timeslot3_model <- lm(positive_p ~ restaurant_access_15 +
                    school_access_25 +
                    hospital_access_25 +
                    busstop_access_70 +
                    greenspace_access_25 +
                    leis_access_20 +
                    public_access_15 +
                    shopping_access_25 +
                    Type +
                    Timeslot +
                    Weather +
                    Timeslot:hospital_access_25,
                    data = weibo_clip)
                  
summary(Timeslot3_model)

# Timeslot4_model <- lm(positive_p ~ restaurant_access_15 +
#                     school_access_25 +
#                     hospital_access_25 +
#                     busstop_access_70 +
#                     greenspace_access_25 +
#                     leis_access_20 +
#                     public_access_15 +
#                     shopping_access_25 +
#                     Type +
#                     Timeslot +
#                     Weather +
#                     Timeslot:busstop_access_70,
#                     data = weibo_clip)
#                   
# summary(Timeslot4_model)
# 
# Timeslot5_model <- lm(positive_p ~ restaurant_access_15 +
#                     school_access_25 +
#                     hospital_access_25 +
#                     busstop_access_70 +
#                     greenspace_access_25 +
#                     leis_access_20 +
#                     public_access_15 +
#                     shopping_access_25 +
#                     Type +
#                     Timeslot +
#                     Weather +
#                     Timeslot:greenspace_access_25,
#                     data = weibo_clip)
#                   
# summary(Timeslot5_model)

Timeslot6_model <- lm(positive_p ~ restaurant_access_15 +
                    school_access_25 +
                    hospital_access_25 +
                    busstop_access_70 +
                    greenspace_access_25 +
                    leis_access_20 +
                    public_access_15 +
                    shopping_access_25 +
                    Type +
                    Timeslot +
                    Weather +
                    Timeslot:leis_access_20,
                    data = weibo_clip)
                  
summary(Timeslot6_model)

# Timeslot7_model <- lm(positive_p ~ restaurant_access_15 +
#                     school_access_25 +
#                     hospital_access_25 +
#                     busstop_access_70 +
#                     greenspace_access_25 +
#                     leis_access_20 +
#                     public_access_15 +
#                     shopping_access_25 +
#                     Type +
#                     Timeslot +
#                     Weather +
#                     Timeslot:public_access_15,
#                     data = weibo_clip)
#                   
# summary(Timeslot7_model)

Timeslot8_model <- lm(positive_p ~ restaurant_access_15 +
                    school_access_25 +
                    hospital_access_25 +
                    busstop_access_70 +
                    greenspace_access_25 +
                    leis_access_20 +
                    public_access_15 +
                    shopping_access_25 +
                    Type +
                    Timeslot +
                    Weather +
                    Timeslot:shopping_access_25,
                    data = weibo_clip)
                  
summary(Timeslot8_model)

# Weather1_model <- lm(positive_p ~ restaurant_access_15 +
#                     school_access_25 +
#                     hospital_access_25 +
#                     busstop_access_70 +
#                     greenspace_access_25 +
#                     leis_access_20 +
#                     public_access_15 +
#                     shopping_access_25 +
#                     Type +
#                     Timeslot +
#                     Weather +
#                     Type:restaurant_access_15,
#                     data = weibo_clip)
#                   
# summary(Weather1_model)

```


# Test the prediction function and see whether the prediction based on same data could produce similar sentiment result.
However, the predicted result lack of data below 0.7.

```{r, message=FALSE, warning=FALSE, results='hide'}
weibo_predict <- weibo_clip %>%
  add_predictions(model = Timeslot8_model) %>%
  select(positive_p, pred)

weibo_predict <- weibo_predict %>%
  mutate(resid = pred - positive_p)

st_error = sd(weibo_predict$resid)

for (i in 1:1000) {
  noisy_pred <- weibo_predict$pred + rnorm(length(weibo_predict$pred), mean=0, sd=st_error)
  noisy_pred = case_when(noisy_pred > 1 ~ 1, 
                                noisy_pred < 0 ~ 0,
                                TRUE ~ noisy_pred) 
  weibo_predict[ , ncol(weibo_predict) + 1] <- noisy_pred 
  colnames(weibo_predict)[ncol(weibo_predict)] <- paste0("noisy_pred_", i)
}


```
  
```{r}
ggplot(weibo_predict, 
       aes(x = positive_p, y = noisy_pred_1)) +
  geom_point(alpha = 0.1, size = 0.1) +
  theme_minimal()
```


```{r}
ggplot(weibo_predict) +
  geom_density(aes(x = positive_p)) +
  geom_density(aes(x = noisy_pred))

```


```{r}
ggplot(weibo_predict) +
  geom_sf(aes(color = weibo_predict$positive_p), size = 0.1) +
  scale_color_viridis_c() +
  theme_map()

ggplot(weibo_clip) +
  geom_sf(aes(color = weibo_clip$positive_p), size = 0.1) +
  scale_color_viridis_c() +
  theme_map()

# predict
# weibo_predict$positive_p
# weibo_clip$positive_p
# write.csv(weibo_predict,"D:\\R sets\\independent-study\\predict.csv")
# write.csv(weibo_clip,"D:\\R sets\\independent-study\\exist.csv")
```

# ```{r, message=FALSE, warning=FALSE, results='hide'}
# test = data.frame(restaurant_access_15, school_access_25, hospital_access_25, busstop_access_70, greenspace_access_25, leis_access_20, public_access_15, shopping_access_25)
# 
# restaurant_access_15 <- weibo_clip$restaurant_access_15
# school_access_25 <- weibo_clip$school_access_25
# hospital_access_25 <- weibo_clip$hospital_access_25
# busstop_access_70 <- weibo_clip$busstop_access_70
# greenspace_access_25 <- weibo_clip$greenspace_access_25
# leis_access_20 <- weibo_clip$leis_access_20
# public_access_15 <- weibo_clip$public_access_15
# shopping_access_25<- weibo_clip$shopping_access_25
# 
# weibo_predict2 <- weibo_clip
# 
# weibo_predict2$positive_p <- predict(full2_model, newdata = test)
# # write.csv(test,"D:\\R sets\\independent-study\\test.csv")
# ```


# Predict based on RANDOM restaurant generated in Arcgis
# Display different sentiment map of resturants based on change of residential and business zoning
```{r, message=FALSE, results='hide'}

for (i in seq(5, 25, by=5)) {
  pl_restaurant_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_pl_restaurant",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(pl_restaurant_access) <- c("id",
                                   paste("pl_restaurant_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(pl_restaurant_access)
}
```

```{r, message=FALSE, warning=FALSE, results='hide'}
weibo_predict <- weibo_clip

weibo_predict$restaurant_access_15 <- weibo_clip$pl_restaurant_access_15

weibo_predict$positive_p <- predict(full2_model, weibo_predict)

ggplot(weibo_predict) +
  geom_sf(aes(color = weibo_predict$positive_p), size = 0.1) +
  scale_color_viridis_c() +
  theme_map()

write.csv(weibo_predict,"D:\\R sets\\independent-study\\predict_pl.csv")

weibo_existing_hist <- ggplot(weibo_clip) +
  geom_histogram(aes(x = positive_p),
                 bins = 30)

weibo_predict_hist <- ggplot(weibo_predict) +
  geom_histogram(aes(x = positive_p),
                 bins = 30)

weibo_existing_hist

weibo_predict_hist

grid.arrange(weibo_existing_hist, weibo_predict_hist,
             ncol = 2)

ggplot(weibo_clip) +
     geom_point(aes(x = restaurant_access_15, y= positive_p))
ggplot(weibo_predict) +
     geom_point(aes(x = restaurant_access_15, y= positive_p))
```

## Prediction of restaurants location based on change of residential and business zones, noticed the planning documents only reflect the conditions of central area of Jiaxing, I intended to replace the restaurants locations within central area, keeping other locations unchanged.


# count restaurant and calculate densities
```{r, message=FALSE, results='hide'}

restaurant_central <- restaurant[centralarea,]

ggplot() +
  geom_sf(data = centralarea, color = "black") +
  geom_sf(data = restaurant_central, color = "red") +
  theme_map()

res_ex_business <- restaurant_central[ex_business,] #create a dataframe that only includes the restaurants that are located within                                               the existing residential and business zones
res_ex_residential <- restaurant_central[ex_residential,]

merge_br <- st_union(ex_business, ex_residential) #create a dataframe that only includes the restaurants that are outside the                                                  existing residential and business zones
ex_other <- st_difference (centralarea, merge_br) 

res_ex_other <- restaurant_central[ex_other,]

# ggplot (ex_other) +
#   geom_sf(data = ex_other, color = "red") +
#   theme_void()

nres_business <- length(res_ex_business$id)
nres_residential <- length(res_ex_residential$id)
nres_other <- length(res_ex_other$id)

area_bus <- set_units(st_area(ex_business), km^2)
den_bus <- as.numeric(nres_business / area_bus)

area_res <- set_units(st_area(ex_residential), km^2)
den_res <- as.numeric(nres_residential / area_res)

area_other <- set_units(st_area(ex_other), km^2)
den_other <- as.numeric(nres_other / area_other)

# area_merge2<- set_units(st_area(merge_br), km^2)
# area_merge2 <- as.numeric(area_merge2)
# area_other2<- set_units(st_area(ex_other), km^2)
# area_other2 <- as.numeric(area_other2)
# area_bus
# area_res
# area_merge2
# area_other2
```
# create random restaurants in planed zoning

```{r, message=FALSE, results='hide'}
sf::sf_use_s2(FALSE)
merge_plbr <- st_union(pl_business, pl_residential) 
ex_plother <- st_difference (centralarea, merge_plbr) 

area_plbus <- set_units(st_area(pl_business), km^2) #calculate areas of planned zonings
area_plres <- set_units(st_area(pl_residential), km^2)
area_plother <- set_units(st_area(ex_plother), km^2)
  
area_plbus <- as.numeric(area_plbus)
area_plres <- as.numeric(area_plres)
area_plother <- as.numeric(area_plother)

area_central<- set_units(st_area(centralarea), km^2)
area_central <- as.numeric(area_central)
area_merge<- set_units(st_area(merge_plbr), km^2)
area_merge <- as.numeric(area_merge)
areasum = area_plbus + area_plres

predict_res_bus <- st_sample(pl_business, 
                             size = area_plbus*den_bus)
predict_res_res <- st_sample(pl_residential, 
                             size = area_plres*den_res)
predict_res_other <- st_sample(ex_plother, 
                             size = area_plother*den_other)
ggplot (pl_business) +
   geom_sf(color = "black") +
   geom_sf(data = predict_res_bus, 
           color = "red",
           size = 0.1) +
   geom_sf(data = predict_res_res,
           color = "blue",
           size = 0.1) +
   geom_sf(data = predict_res_other,
           color = "green",
           size = 0.1) +
   theme_void()

## replace the predicted restaurant with existed ones within central area
outsidecentral <- st_difference (boundary, centralarea)
restaurant_outcentral <- restaurant[outsidecentral,]

ggplot() +
  geom_sf(data = centralarea, color = "black") +
  geom_sf(data = restaurant_outcentral, color = "red") +
  theme_map()

predict_res_bus_df <- tibble(zone = rep("business", 
                                      length(predict_res_bus))) %>%
  st_sf(geometry = predict_res_bus)

predict_res_res_df <- tibble(zone = rep("residential", 
                                      length(predict_res_res))) %>%
  st_sf(geometry = predict_res_res)

predict_res_other_df <- tibble(zone = rep("other", 
                                      length(predict_res_other))) %>%
  st_sf(geometry = predict_res_other)

predict_res_in <- rbind(predict_res_bus_df, predict_res_res_df, predict_res_other_df)

predict_res_in <- predict_res_in %>% 
  st_transform("WGS84")
restaurant_outcentral <- restaurant_outcentral %>% 
  st_transform("WGS84")

restaurant_outcentral <- restaurant_outcentral %>%
  mutate(zone = "outside")

restaurant_outcentral <- restaurant_outcentral %>%
  st_zm()

# the following chuck is for achieve rbind.fill function without loading the plyr package, the reason why not loading this package because if I loaded this, the accessibility function can not be runned due to the overlap function of two loaded package

rbindx <- function(..., dfs=list(...)) {   
  ns <- unique(unlist(sapply(dfs, names)))
  do.call(rbind, lapply(dfs, function(x) {
    for(n in ns[! ns %in% names(x)]) {x[[n]] <- NA}; x }))
}

predict_res <- rbindx(predict_res_in, restaurant_outcentral)

predict_res_point <- st_as_sf(x = predict_res, 
                        crs = "WGS84")

ggplot (restaurant) +
   geom_sf(color = "black") +
   theme_void()

ggplot (predict_res_point) +
   geom_sf(color = "red") +
   theme_void()
```

## get number of predicted restaurants in each grid cell

```{r}
grid <- grid %>%
  mutate(num_predict_res = lengths(st_covers(grid,predict_res_point)))

grid_points <- st_centroid(grid)

```
# estimate sentiment map based on predicted restaurant
# Display different sentiment map of resturants based on change of residential and business zoning
```{r, message=FALSE, results='hide'}

for (i in seq(5, 25, by=5)) {
  pr_restaurant_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_predict_res",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(pr_restaurant_access) <- c("id",
                                   paste("pr_restaurant_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(pr_restaurant_access)
}
```
```{r, message=FALSE, warning=FALSE, results='hide'}
weibo_predict2 <- weibo_clip

weibo_predict2$restaurant_access_15 <- weibo_clip$pr_restaurant_access_15

weibo_predict2$positive_p <- predict(full2_model, weibo_predict2)

ggplot(weibo_predict2) +
  geom_sf(aes(color = weibo_predict2$positive_p), size = 0.1) +
  scale_color_viridis_c() +
  theme_map()

# write.csv(weibo_predict,"D:\\R sets\\independent-study\\predict_pl.csv")

weibo_existing_hist <- ggplot(weibo_clip) +
  geom_histogram(aes(x = positive_p),
                 bins = 30)

weibo_predict2_hist <- ggplot(weibo_predict2) +
  geom_histogram(aes(x = positive_p),
                 bins = 30)

weibo_existing_hist

weibo_predict2_hist

grid.arrange(weibo_existing_hist, weibo_predict_hist,
             ncol = 2)

ggplot(weibo_clip) +
     geom_point(aes(x = restaurant_access_15, y= positive_p))
ggplot(weibo_predict2) +
     geom_point(aes(x = restaurant_access_15, y= positive_p))
```

## scenario 2: double the number of school spreading out the city
```{r, message=FALSE, warning=FALSE, results='hide'}
nschool <- length(school$id)
newschool <- st_sample(boundary, 
                             size = nschool)

newschool_df <- tibble(type = rep("new", 
                                      length(newschool))) %>%
  st_sf(geometry = newschool)

doubleschool <- rbindx(newschool_df, school)

doubleschool_point <- st_as_sf(x = doubleschool, 
                        crs = "WGS84")
```
## get number of doublesschool in each grid cell and calculate accessibility with best fit

```{r}
grid <- grid %>%
  mutate(num_doubleschool = lengths(st_covers(grid,doubleschool_point)))

grid_points <- st_centroid(grid)

for (i in seq(20, 30, by=5)) {
  doubleschool_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_doubleschool",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(doubleschool_access) <- c("id",
                                   paste("doubleschool_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(doubleschool_access)
}

weibo_predict_scenario2 <- weibo_clip

weibo_predict_scenario2$doubleschool_access_25 <- weibo_clip$doubleschool_access_25

weibo_predict_scenario2$positive_p <- predict(full2_model, weibo_predict_scenario2)

ggplot(weibo_predict_scenario2) +
  geom_sf(aes(color = weibo_predict_scenario2$positive_p), size = 0.1) +
  scale_color_viridis_c() +
  theme_map()
```
## scenario 3: turn school into greenspace
```{r, message=FALSE, warning=FALSE, results='hide'}

transgreen <- school

newgreen <- rbindx(transgreen, greenspace)

newgreen_point <- st_as_sf(x = newgreen, 
                        crs = "WGS84")
```
## get number of newgreenspace in each grid cell and calculate accessibility of greenspace with best fit and make the accessibility of school as 0 due to removal of school in Jiaxing

```{r}
grid <- grid %>%
  mutate(num_newgreen = lengths(st_covers(grid,newgreen_point)))

grid_points <- st_centroid(grid)

for (i in seq(20, 30, by=5)) {
  newgreen_access <- accessibility(r5r_core,
                                   origins = weibo_clip,
                                   destinations = grid_points,
                                   opportunities_colname = "num_newgreen",
                                   mode = "WALK",
                                   decay_function = "step",
                                   cutoffs = i,
                                   verbose = FALSE) %>%
    mutate(id = as.numeric(from_id)) %>%
    select("id", "accessibility")

  colnames(newgreen_access) <- c("id",
                                   paste("newgreen_access_", i, sep = ""))

  weibo_clip <- weibo_clip %>%
    left_join(newgreen_access)
}

weibo_predict_scenario3 <- weibo_clip

weibo_predict_scenario3$newgreen_access_25 <- weibo_clip$newgreen_access_25
weibo_predict_scenario3$school_access_25 <- 0

weibo_predict_scenario3$positive_p <- predict(full2_model, weibo_predict_scenario3)

ggplot(weibo_predict_scenario3) +
  geom_sf(aes(color = weibo_predict_scenario3$positive_p), size = 0.1) +
  scale_color_viridis_c() +
  theme_map()
```
  